A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-08-05 paper.tex
Fix grammar and typos

\begin{abstract} 
%cite IoT data subscription economy
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

\section{Introduction}
As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the existing solutions targeting in static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading.
Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
\end{itemize}

Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

@@

\section{Related Work}
\label{section:relatedWork}
G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. The data validation and traceability are achieved via Ethereum smart contract. But data is plaintext on blockchain that the system is not appropriate for sensitive data.

Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. Yet, without brokers, participants may need to reveal more sensitive information in order to communicate. By Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single point failure still exists.

Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer. The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams. It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.

@@

Centralized identity model may have single point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.

\subsection{Enable Automated Trading Process}
With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures. Product Contract records the MAM channel/endpoint ID of both DID document of participants and the data stream. The subscription and brokerage fee, and the broker-certified encryption key are listed on Product Contract as well.

@@

\section{Masked Authenticated Messaging}
\label{section:MAM}
With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage. Section.~\ref{section:mam_streams} and ~\ref{section:mam_features} explain the structure, fuctions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.

\subsection{The Message Streams}
\label{section:mam_streams}
A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle, represents the ownership of all things associated with the user in the IOTA ecosystem.

The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint. Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data. Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.

@@

\subsection{Enable Access Control and Authentication}
\label{section:mam_features}
The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels. If the message payload is encrypted, subscribers are required for encryption keys to decode messages. The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender. These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of MAM bundle. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

\subsection{Delegate MAM operations to Accel}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

\subsubsection{End-to-End-Encryption}
Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message. To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol. The plaintext will be encrypted with this lightweight end-to-end-encryption. The E2EE process ensures only authorized subscribers can read the messages published on MAM.

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:

\begin{enumerate}
    \item Generate symmetric keys with unique device identifier and Message Authentication Code (MAC) of the previous message. If the message is the genesis message, then a sharing secret initialization information would serve as the MAC of previous message. Key Derivation Function (KDF) is used to generate the symmetric keys.
    \item Compute the Message Authentication Code (MAC) of current message with Hash-based Message Authentication Code(HMAC). Both plaintext and symmetric key would be given as parameters in HMAC.
    \item Apply the generated symmetric key to encrypt plaintext.
    \item Concatenate the MAC of current message would and the MAC of previous message, and then the result will be signed with digital signature algorithm.
    \item Send the ciphertext along with signed MAC.
\end{enumerate}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and ECDSA P-256 for digital signature. In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which cause the time complexity is $O(n)$, too. Therefore, the E2EE protocol takes only linear time versus arbitrary string length.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge device utilizing blockchain service. It dramatically reduces execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to a Accel which is operated by unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers wasting plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to an known, trustworthy Accel would be the easiest solution.

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription. A discussion of refund is illustrated.

\subsection{Prerequisite}
All participants are required to register on TangleID to get DID document and public/private key pair for sensitive contents exchange and authentication. An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.

\subsection{Launch Data Products}
To launch a data product, brokers are responsible to create Product Contract and record the metadatas of data product for data providers. The Product Contract will not accept subscriptions until brokers certify the encryption key. To certify the encryption key, the data provider first computes its digest with hash function, and sends the digest as well as the signature to brokers. The broker verify the signature with the public key on provider's DID document. If it's valid, the broker will sign and upload the key to Product Contract, otherwise the process will be aborted. The number of key uploading time is restricted in order to avoid data provider uploading fake keys frequently. If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to Product Contract via a broker. Finally, the data product is launched and data providers can start uploading data.
\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

\subsection{Subscribe to Data Product}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can decode it.

Transferring the encryption key on smart contract instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to public. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange}. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.

@@

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics is complicated in a subscription services, therefore, we illustrated the challenges in this section. As the subscription-based services in real world, participants can launch a refund in following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as, consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can not reach a consensus of the brokerage fee during subsription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they fail to maintain products as committed.

@@

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes: 1.) \textbf{Tips selection}: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes. 2.) \textbf{Proof-of-Work (PoW)}: An algorithm which prevents Denial of Service and spam attacks on a network.

>>>>

\begin{abstract}
%cite IoT data subscription economy
On top of subscription-based pricing models such as Software-as-a-Service (SaaS), monetizing the subscription enables the payment of data streams with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data collections, the streaming data increases difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing, and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

\section{Introduction}
As the physical and digital data are deeply intertwined in IoT, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, the data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the existing solutions targeting static data sets\cite{DIaas, MARSA}, this paper aims for processing the high volume, high velocity, and high variety of real-time data streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading.
Among the challenges of data trading platform\cite{BigDataMarket}, the following characteristics are required:
\begin{itemize}
    \item \textbf{Scalability}.
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible.
    \item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.
    \item \textbf{Confidentiality}.
1) Only the authorized participants can access data streams. 2) Participants that have access can always retrieve data even if they're dropped from the network.
    \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
\end{itemize}

Taking all the requirements into consideration, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure as shown in Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts written on DLTs are transparent, immutable, and enforced automatically, which allows devices to focus on their jobs while gaining the rewards. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.

@@

\section{Related Work}
\label{section:relatedWork}
G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. Data validation and traceability are achieved via the Ethereum smart contract. But data is plaintext on blockchain that the system is not appropriate for sensitive data.

Secure Pub-Sub model\cite{SPS}, a brokerless design, is proposed to eliminate the security risk of middleware and to provide a reputation-based fairness payment strategy on blockchain.
The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent. Yet, without brokers, participants may need to reveal more sensitive information in order to communicate. By Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of data information) are stored in a centralized Cassandra database, guaranteed to be tamper-proof but the risk of single-point failure still exists.

Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof, and authentication functionalities by tailoring messages to a channel. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading in IOTA token and applies MAM as the data storage and data transmission layer. The decentralized data marketplace\cite{DDMSmartCities} is operated without any intermediate server but data providers only, data providers attach, and trade data streams via MAM. Nevertheless, the above works did not take into account the refund and unsubscribe mechanism of the trading model.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data consists of continually granular records of each time slot. Therefore, the verification such as data integrity and source identity is narrow down to a data point as well. In our proposed architecture, MAM is adopted as data storage to resolve the challenges of managing and verifying data streams by implementing the second layer data communication protocol built on top of the IOTA network, the Tangle, which has properties like publishing, classifying and tracking authenticated message streams. It builds the trust of the platform while meeting the requirements of IoT streaming data storage which can be concluded: 1) \textbf{Scalability}, for both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible. 2) \textbf{Integrity}, messages were written on the Tangle are immutable. 3) \textbf{Confidentiality}, the message can be encrypted with an \textbf{encryption key} that restricts only authorized players can access contents. 4) \textbf{Proof of Ownership}, signing messages with \textbf{signature key} generated from Merkle signature scheme\cite{MSS} (MSS) allows users to ensure them originated from the same source by validating the signatures without knowing the actual contents. See Fig.~\ref{fig:channel_and_key} for illustration.

@@

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing content to the IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.

@@

A centralized identity model may have the single-point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, whether the data leakage is caused by cyber-attacks or unscrupulous organizations trading user data, the users' privacy is damaged. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.

@@

Through TangleID, entities get a public/private key pair, the location of DID document, and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish trust communication, where messages that are encrypted with a public key can only be decrypted with the private key owner. During the data subscription process, the encryption keys of data products are transmitted with the public key on the DID document.

\subsection{Enable Automated Trading Process}
With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} contains the metadata of a data product and defines the trading procedures. Product Contract records the MAM channel/endpoint ID of both the DID document of participants and the data stream. The subscription and brokerage fee, and the broker-certified encryption key are listed on the Product Contract as well.

@@

\section{Masked Authenticated Messaging}
\label{section:MAM}
With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage. Section.~\ref{section:mam_streams} and ~\ref{section:mam_features} explain the structure, functions and features of MAM proposed by IOTA Foundation, and our proposed MAM delegation mechanism is clarified in Section.~\ref{section:ta_endpoint}.

\subsection{The Message Streams}
\label{section:mam_streams}
A channel/endpoint is a stream of MAM transaction bundles, consisting of signature and the masked message payload. To publish a MAM message to the channel, MAM deploys MSS to sign the message payload to the channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the Tangle represents the ownership of all things associated with the user in the IOTA ecosystem.

The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of the MAM channel/endpoint. Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data. Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.

@@

\subsection{Enable Access Control and Authentication}
\label{section:mam_features}
The access control can be enabled via encryption with NTRU\cite{NTRU}, a quantum secure cryptosystem, or Pre-shared key (PSK), to prevent random users retrieving the data from channels. If the message payload is encrypted, subscribers are required for encryption keys to decode messages. The authentication in MAM includes two aspects: source and data. Source authentication ensures the message that originates from the claimed owner, and data authentication ensures the integrity of the data from the sender. These are achieved through the MSS and One-way hash functions by validating the signature added in the signature section of the MAM bundle. However, the size of Merkle Hash Trees, that is, the size of a channel/endpoint should be determined at the start. Thus, data providers need to first decide how to distribute data products into MAM channels/endpoints before uploading data.

\subsection{Delegate MAM operations to Accel}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources with, and they may not even support built-in libraries in regular operating systems. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Accel, proxy servers with high computation power, which can accelerate the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

\subsubsection{End-to-End-Encryption}
Introducing a proxy server to process all the cryptographic operations causes the proxy server or the middle man can easily tamper the message. To avoid such malicious operations during transmission, we introduce another lightweight end-to-end-encryption (E2EE) upon MAM protocol. The plaintext will be encrypted with this lightweight end-to-end-encryption. The E2EE process ensures that only authorized subscribers can read the messages published on MAM.

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of the steps are addressed below:

\begin{enumerate}
    \item Generate symmetric keys with a unique device identifier and Message Authentication Code (MAC) of the previous message. If the message is the genesis message, then sharing secret initialization information would serve as the MAC of the previous message. Key Derivation Function (KDF) is used to generate the symmetric keys.
    \item Compute the Message Authentication Code (MAC) of the current message with the Hash-based Message Authentication Code(HMAC). Both plaintext and the symmetric key would be given as parameters in HMAC.
    \item Apply the generated symmetric key to encrypt the plaintext.
    \item Concatenate the MAC of the current message would and the MAC of the previous message, and then the result will be signed with a digital signature algorithm.
    \item Send the ciphertext along with signed MAC.
\end{enumerate}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On certain devices, hardware acceleration would be supported. With hardware-acceleration, the elapsed time could be dropped a step more. For example, applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Some popular microcontrollers have integrated hardware accelerators for AES as well.\cite{stm}

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and ECDSA P-256 for digital signature. In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too. Therefore, the E2EE protocol takes only linear time versus arbitrary string length.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge devices utilizing blockchain service. It dramatically reduces the execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to an Accel which is operated by an unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers to waste plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to a known, trustworthy Accel would be the easiest solution.

\section{Decentralized Subscription-based Data Trading Models}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel the subscription. A discussion of refunds is illustrated.

\subsection{Prerequisite}
All participants are required to register on TangleID to get a DID document and public/private key pair for sensitive contents exchange and authentication. An Ethereum account is also needed to interact with smart contracts and transfer Ethereum tokens.

\subsection{Launch Data Products}
To launch a data product, brokers are responsible to create a Product Contract and record the metadata of the data product for data providers. The Product Contract will not accept subscriptions until brokers certify the encryption key. To certify the encryption key, the data provider first computes its digest with the hash function and sends the digest as well as the signature to brokers. The broker verifies the signature with the public key on the provider's DID document. If it's valid, the broker will sign and upload the key to the Product Contract, otherwise, the process will be aborted. The number of key uploading times is restricted in order to avoid data provider uploading fake keys frequently. If data consumers find out the encryption key does not match the provider's signature after payment, they can request a refund. Fig.~\ref{fig:key_upload} demonstrates the key uploading process to the Product Contract via a broker. Finally, the data product is launched and data providers can start uploading data.
\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of the encryption key and the one that signed with his/her private key. After the broker receive the request, he/she signs it as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

\subsection{Subscribe to Data Product}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the encryption key of data stream instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by the data provider and written on the Product Contract, which ensures only data consumers can decode it.

Transferring the encryption key on smart contracts instead of off-chain not only ensures the consistency of the encryption key but also prevents frauds from malicious participants, and the exchange process is transparent to the public. Furthermore, with the help of brokers and smart contracts, both data providers and consumers do not need to be online at the same time to proceed with the trading process. The key sending process is shown in Fig.~\ref{fig:key_exchange}. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM.

@@

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics are complicated in subscription services, therefore, we illustrated the challenges in this section. As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they fail to maintain products as committed.

@@

\subsubsection{Messages Publishment}
Publishing a message to MAM is attaching a zero-value transaction to the Tangle which requires two processes: 1.) \textbf{Tips selection}: In the IOTA protocol, a new-coming transaction needs to pick up 2 existed transactions called tips to reference and verify. The tips are provided by IOTA full nodes. 2.) \textbf{Proof-of-Work (PoW)}: An algorithm that prevents Denial of Service and spam attacks on a network.
